\documentclass{article}
\usepackage{hyperref}

\input{info.tex}

\begin{document}

\begin{center}
    \textbf{Dear \HiringManager},
\end{center}

I am writing to express my interest in the \PositionTitle position at \CompanyName. As a current student pursuing a Bachelor of Science degree in Computer Engineering at Middle East Technical University, I am eager to contribute to your team as a computer engineer.

Throughout my academic journey, I have been dedicated to expanding my knowledge and skills in computer science and software development. I have gained a strong foundation in computer science principles and acquired proficiency in various programming languages and technologies, including Python, C/C++, JavaScript, and SQL. Relevant coursework in Database Management Systems and Object-oriented Programming Languages has equipped me with the necessary skills to excel in a software engineering role.

In addition to my academic pursuits, I have actively sought opportunities to apply my skills in real-world settings. As a Computer Engineer at Oruba Technology and Innovation, I had the privilege of working on diverse projects and contributing to the development of features for device applications using Vue.js and Python. This hands-on experience has strengthened my problem-solving abilities and prepared me for the challenges of a professional software engineering environment.

Thank you for considering my application. I am enthusiastic about the opportunity to discuss how my background, skills, and passion for software engineering align with the needs of \CompanyName. I am available for an interview at your earliest convenience and can be reached at \YourPhoneNumber or via email at \YourEmailAddress.

Sincerely,

\YourName

\end{document}
