\documentclass[11pt]{article}
\usepackage{graphicx} % Required for inserting images
\setlength{\parindent}{0pt}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage[utf8]{inputenc} 
\usepackage[T1]{fontenc}
\usepackage[brazil]{babel}
\usepackage{lipsum}
\usepackage[left=1.06cm,top=1.7cm,right=1.06cm,bottom=0.49cm]{geometry}
\usepackage{xcolor}




%by: Aline R. Antunes

\begin{document}
\begin{center}
    \textbf{Atakan Önol}\\ 
    \hrulefill
\end{center}

\begin{center}
    Ankara, Türkiye \textbullet \href{mailto:me@atakanonol.dev}{me@atakanonol.dev} \textbullet +90 (535) 014-6266 \textbullet \href{https://github.com/aslansutu}{github.com/aslansutu} \\
    Gaithersburg, MD 20879 \textbullet \href{mailto:atakan16@gmail.com}{atakan16@gmail.com} \textbullet +1 (919) 888-8974 \textbullet \href{https://atakanonol.dev}{atakanonol.dev} \\
\end{center}

\vspace{0.5pt}

\begin{center}
    \textbf{Education}
\end{center}
\textbf{Middle East Technical University} \hfill Ankara, Türkiye

B.Sc. Computer Engineering \hfill 2014-Present

\vspace{12pt}

\begin{center}
    \textbf{Experience}
\end{center}
\textbf{Oruba Technology and Innovation} \hfill Ankara, Türkiye

\textbf{Computer Engineer} \hfill March 2021 – Present
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Spearheaded the development of innovative features by harnessing Vue.js for frontend and Python for backend, bolstering the functionality and user experience of the device application.
    \item Demonstrated design prowess by building the company’s website from the ground up, ensuring an engaging and informative online presence.
    \item Leveraged cutting-edge WebXR technology to create an immersive VR game, controlled through electrodes, showcasing the company’s technological prowess.
    \item Pioneered the implementation of an efficient update mechanism for IoT devices using Mender.IoT, streamlining device maintenance, software updates, and critical security patches.
    \item Navigated the complexities of remote technical support, offering comprehensive assistance to clients both domestically and internationally.
    \item Played a pivotal role in the onboarding process by mentoring and training incoming interns, fostering a culture of knowledge sharing and skill development.
\end{itemize}

\vspace{12pt}

\textbf{MarketSource} \hfill Raleigh, North Carolina

\textbf{Outside Sales Representative} \hfill September 2013 – July 2014
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Proactively engaged customers within retail locations to promote and sell HP products, accessories, and digital services, focusing on driving sales productivity and customer satisfaction.
    \item Trained retail associates about new HP products and features.
    %\item Collaborated with retail associates in side-by-side selling to effectively showcase the features and benefits of HP products and services.
    %\item Participated in in-store promotions and sales events, coordinating with appropriate personnel to maximize sales opportunities.
    %\item Maintained up-to-date knowledge of HP's product portfolio, including laptops, desktops, printers, and accessories, to provide accurate information and recommendations to customers.
    %\item Attended training sessions and conference calls to stay informed about new HP product releases, features, and promotions.
    %\item Established and managed positive business relationships with retail store management and employees.
\end{itemize}


\textbf{Triangle Aquatic Center} \hfill Cary, North Carolina

\textbf{Lifeguard} \hfill March 2012 – July 2014
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Executed water rescues and administered first aid or CPR as needed.
    \item Maintained detailed records of emergency medical treatments.
    %\item Ensured the cleanliness of recreational facilities.
    \item Conducted routine pool water testing and chemical adjustments.
\end{itemize}

% \begin{center}
%     \textbf{Leadership \& Activities}
% \end{center}

% \textbf{Organization}	\hfill City, State

% \textbf{Role} \hfill Month Year – Month Year
% \begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
%     \item Executed water rescues and administered first aid or CPR as needed.
%     \item Maintained detailed records of emergency medical treatments.
%     \item Ensured the cleanliness of recreational facilities.
%     \item Conducted routine pool water testing and chemical adjustments.
% \end{itemize}

\begin{center}
    \textbf{Skills \& Interests}
\end{center}

\textbf{Technical:} Python, C/C++, SQL, LaTeX, Java, HTML, CSS, Javascript, VueJS, Flask, Docker, Git

\textbf{Language:} English (Native), Turkish (Native)

%\textbf{Laboratory:} List scientific / research lab techniques or tools [If Applicable]

\textbf{Interests:} Chess, DIY Projects, Sports (American Football, Swimming, Water Polo, Skiing, Basketball among many others), Camping, Cooking, Guitar, Homelab, Motorcycles




\end{document}
